Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-18 qhtv2.tex
+FNR
typos

\section{Queuing filters}
In this section, we describe the queuing construction, which produces a sliding window DDF from any DDF. We first give the description of the setup, before studying the theoretical error rates. 
A scheme describing our structure is detailed in \ref{fig:scheme}.

@@

\paragraph{Pseudocode.}
We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in \ref{alg:queueing}. We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$. The \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first  position.

@@

\paragraph{Remark.}
	\label{subsub:number_elements}
	By definition, after $c$ insertions the last subfilter is dropped.
Information-theoretically, this means that all the information related to the elements inserted in that subfilter has been lost, and there are $c$ such elements by design. 
Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements(immediatey after deleting the last subfilter) and at most $cL$ elements (immediately before this deletion).

@@

\subsection{DDF Comparison}
A filter comparison was already made in \cite{10.1145/3297280.3297335}. Taking the same filters parameters, created another benchmark, studying the resistance of each DDF to saturation. We added the lower bound on the error rate. More details about the experiments are given in \ref{sub:saturation}. We observe in \ref{fig:graph_n} that the two most efficient filters are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.

However, as noted in \ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters. Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.

@@

We have observed in \ref{sub:fnr} that the FN is positively correlated with
$\left(1-\FP_{\mathcal F,c}\right)^L$, however the FP is negatively correlated with the same value. As such, decreasing the probability of false positive leads to an increase in the probability of false negatives.

\todo[FAUX, peut etre log ? However, practical tests show (see \ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]

@@

We remind the reader that for small sliding windows compared to the memory size, optimal or nearly optimal solutions can be implemented, as discussed in \ref{sub:opt_solutions}. However, since we must evaluate the number of duplicates in the streams we use, we cannot benchmark our filter in real-life situations, as doing so would require way too much memory for keeping track of the duplicates.

@@

The stream was a stream of uniform random elements, taken from an alphabet of $2^{26}$ elements, and amounts for about 8\% duplicates on the 150 000 000 elements in the longest stream used. Results are plotted in \ref{fig:graph_n}.

@@

\subsection{Benchmarking Various Queuing Filters}
Now that DDF are compared on a full stream, we observe how each of them behave when they act as a subfilter in our queueing scheme. The goal is to empirically prove the assumption made in \ref{sub:optimal_ddf}, stating that the best (error-wise) DDF operating on a full stream leads to the best (error-wise) queueing filter operating on a sliding window. From \ref{fig:graph_n}, we observe that the best DDF for DDP on a full stream are, in order, QHT, SQF, Cuckoo, SQF.

@@

We used a random stream of $1,000,000$ elements uniformly selected from an alphabet of size $|\Gamma| = 2^{16}$, a memory size $M=100,000$ bits, a sliding window of size $w = 10,000$. The error rates (defined as the sum of $\FNR^w$ and $\FPR^w$) are displayed in \ref{tab:comparing_queueing}. We see that in all cases, the QHT subfilter performs better or almost as well than any other subfilter, hence validating the heuristic assumption.

>>>>

\section{Queuing filters}
In this section, we describe the queuing construction, which produces a sliding window DDF from any DDF. We first give the description of the setup, before studying the theoretical error rates. 
A scheme describing our structure is detailed in Figure~\ref{fig:scheme}.

@@

\paragraph{Pseudocode.}
We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in Algorithm~\ref{alg:queueing}. We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$. The \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first  position.

@@

\paragraph{Remark.}
	\label{subsub:number_elements}
	By definition, after $c$ insertions the last subfilter is dropped.
Information-theoretically, this means that all the information related to the elements inserted in that subfilter has been lost, and there are $c$ such elements by design. 
Therefore, in the steady-state regime, the queuing filter holds information about at least $c(L-1)$  elements (immediately after deleting the last subfilter) and at most $cL$ elements (immediately before this deletion).

@@

\subsection{DDF Comparison}
A filter comparison was already made in \cite{10.1145/3297280.3297335}. Taking the same filters parameters, created another benchmark, studying the resistance of each DDF to saturation. We added the lower bound on the error rate. More details about the experiments are given in Section~\ref{sub:saturation}. We observe in Figure~\ref{fig:graph_n} that the two most efficient filters are the QHT \cite{10.1145/3297280.3297335} and the A2 \cite{Yoo10}.

However, as noted in Section~\ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters. Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.

@@

We have observed in Section~\ref{sub:fnr} that the FN is positively correlated with
$\left(1-\FP_{\mathcal F,c}\right)^L$, however the FP is negatively correlated with the same value. As such, decreasing the probability of false positive leads to an increase in the probability of false negatives.

\todo[FAUX, peut etre log ? However, practical tests show (see Section~\ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]

@@

We remind the reader that for small sliding windows compared to the memory size, optimal or nearly optimal solutions can be implemented, as discussed in Section~\ref{sub:opt_solutions}. However, since we must evaluate the number of duplicates in the streams we use, we cannot benchmark our filter in real-life situations, as doing so would require way too much memory for keeping track of the duplicates.

@@

The stream was a stream of uniform random elements, taken from an alphabet of $2^{26}$ elements, and amounts for about 8\% duplicates on the 150 000 000 elements in the longest stream used. Results are plotted in Figure~\ref{fig:graph_n}.

@@

\subsection{Benchmarking Various Queuing Filters}
Now that DDF are compared on a full stream, we observe how each of them behave when they act as a subfilter in our queueing scheme. The goal is to empirically prove the assumption made in Section~\ref{sub:optimal_ddf}, stating that the best (error-wise) DDF operating on a full stream leads to the best (error-wise) queueing filter operating on a sliding window. From Figure~\ref{fig:graph_n}, we observe that the best DDF for DDP on a full stream are, in order, QHT, SQF, Cuckoo, SQF.

@@

We used a random stream of $1,000,000$ elements uniformly selected from an alphabet of size $|\Gamma| = 2^{16}$, a memory size $M=100,000$ bits, a sliding window of size $w = 10,000$. The error rates (defined as the sum of $\FNR^w$ and $\FPR^w$) are displayed in Table~\ref{tab:comparing_queueing}. We see that in all cases, the QHT subfilter performs better or almost as well than any other subfilter, hence validating the heuristic assumption.
